\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-09-25 parts-infer-ig.tex
section 4

\todo{The reviewer says about the following paragraph: “The inference of an
IG from a dynamics is interesting and important in biology. However the
motivations expressed here are not well argued. In particular I don't find
this “common”. Some bibliographical references are required to consolidate
the arguments or the sentence has to be rephrased.”}

In a typical biological network modeling process, a prior IG is generally the starting point for
the formal system specification.
However, it is common that the prior IG actually refers to interactions that reveal to be 
non-effective with respect to the dynamics.
Hence, deriving the IG directly from the dynamical models lead to more concise IGs, enhancing the
conclusiveness of static analyses based upon this abstract representation.

>>>>

\modLP{The inference of the IG also allows to check for the
consistency of the model with respect to prior knowledge on the influences.
This is the case for Thomas models, where a prior IG is required to specify the 
parameters of the dynamics.
Following \todo{ref Adrien, autre}, the IG of a dynamical model is consistent
with a prior IG if it is a sub-graph of the prior IG.
On the one hand, having influences in the model not references in the prior IG
indicates either mistakes in the encoding of the dynamics, or potential
influences that might need to be verified in the biological system.
One the other hand, some influences specified in the prior IG may not have been
necessary to encode the desired dynamics, indicating some non-minimality of the
prior IG \todo{more refs}.}
